Report on a Safety Checker for Petri nets

### 2013-11-25 paper/workspace/main.tex
Experimental setup and report for IIC.

\newcommand{\bfc}{{\sc Bfc}}
\newcommand{\mist}{{\sc Mist}}
\newcommand{\pnerf}{{\sc Pnerf}}
\newcommand{\zthree}{{\sc Z3}}
\newcommand{\ttt}[1]{\texttt{#1}}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{7cm} | r | r | r | r | } %
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 23 &  0 & 54 &  0 \\
    Invariant                              & 23 &  0 & 54 &  0 \\
    Invariant Minimization                 & 23 &  0 & 54 &  0 \\
    Safety by Refinement                   & 23 &  0 & 54 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \bfc}
\label{bfc-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 14 &  0 & 13 &  0 \\
    Invariant                              & 14 &  0 & 13 &  0 \\
    Invariant Minimization                 & 14 &  0 & 13 &  0 \\
    Safety by Refinement                   & 20 &  0 &  7 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

>>>>

\newcommand{\bfc}{{\sc Bfc}}
\newcommand{\mist}{{\sc Mist}}
\newcommand{\iic}{{\sc IIC}}
\newcommand{\pnerf}{{\sc Pnerf}}
\newcommand{\zthree}{{\sc Z3}}
\newcommand{\ttt}[1]{\texttt{#1}}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{7cm} | r | r | r | r | } %
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 23 &  0 & 54 &  0 \\
    Invariant \& Invariant Minimization    & 23 &  0 & 54 &  0 \\
    Safety by Refinement                   & 23 &  0 & 54 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \bfc}
\label{bfc-experiments}
\end{table}

@@

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 14 &  0 & 13 &  0 \\
    Invariant \& Invariant Minimization    & 14 &  0 & 13 &  0 \\
    Safety by Refinement                   & 20 &  0 &  7 &  0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \mist}
\label{mist-experiments}
\end{table}

\section{Benchmarks of \iic}

We experimented on the benchmarks available at \\
\ttt{https://svn.rse.mpi-sws.org/RSE/IC3forWSTS/code/trunk/examples/soter}.
The set of benchmarks consists 38 benchmarks, 28 positive and 10 negative.
Table~\ref{iic-experiments} shows the corresponding experimental results.

\begin{table}[h]
\begin{center}
  \begin{tabular}{ | p{6cm} | r | r | r | r | }
    \hline
    Method & pos & neg & don't know & TO \\
    \hline
    Safety (over real numbers or naturals) & 2 & 0 & 36 & 0 \\
    Invariant \& Invariant Minimization    & 2 & 0 & 26 & 0 \\
    Safety by Refinement                   & 2 & 0 & 36 & 0 \\
    \hline
  \end{tabular}
\end{center}
\caption{Experimental results for the benchmarks of \iic}
\label{iic-experiments}
\end{table}
